%-------------------------
%The MIT License (MIT)
%
%Copyright (c) 2015 Sourabh Bajaj
%
%Permission is hereby granted, free of charge, to any person obtaining a copy
%of this software and associated documentation files (the "Software"), to deal
%in the Software without restriction, including without limitation the rights
%to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%copies of the Software, and to permit persons to whom the Software is
%furnished to do so, subject to the following conditions:
%
%The above copyright notice and this permission notice shall be included in all
%copies or substantial portions of the Software.
%
%THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%SOFTWARE.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\multicomment}[1]{}

\newcommand{\Section}[1]{\textbf{\section*{#1}}}

\newcommand{\resumeItem}[2]{
  \item[] \small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  	\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-12pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
	\textbf{{\LARGE Garrett Hay}}
\end{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l c c r}
	\href{github.com/Garrett-H}{github.com/Garrett-H} & \href{mailto:garretthay97@gmail.com}{garretthay97@gmail.com} & +1-731-446-9792 & \href{linkedin.com/in/garretthay} {linkedin.com/in/garretthay} \\
\end{tabular*}
%-----------OBJECTIVE------------------
\Section{Summary}
\begin{itemize}[noitemsep,nolistsep] \small 
    	\item[$\circ$] Recent graduate of Computer Science
    	\item[$\circ$] 4+ years experience as IT Specialist and web assistant
    	\item[$\circ$] Organized contributor able to meet goals independently or within a team
    	\item[$\circ$] Experienced in Agile Production methodology 
    \end{itemize}
    \vspace{-18pt}
%As a recent graduate of Computer Science specializing in configuration \& repair with 3+ years experience as IT Specialist, seeking an organization where I can help users in both software support \& development.  

%-----------EDUCATION-----------------
\Section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Tennessee at Martin}{Martin, TN} %3.38
      {BS in Computer Science}{Anticipated Graduation: \textbf{May 2020}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\Section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading
	{UT Martin Information Technology}{Martin, TN}
	{Support Technician Assistant}{June 2016 - July 2020}
    \resumeItemListStart
    	\resumeItem{Field Services}
        { Preparation, installation, \& continued support/repair of Windows, Apple, \& Linux computers, scanners, printers, \& any included accessories for staff \& faculty of UT Martin. Assisted in training of new hire Student Assistants.}
        \resumeItem{Web Development Assistant} {Continuous development of University's website through PHP.}
     \resumeItemListEnd     
     
     
     \resumeSubheading
	{Baptist Memorial Hospital}{Union City, TN}
	{IT Generalist I}{July 2020-Current}
    \resumeItemListStart
        \resumeItem{Site Support} { Troubleshooting, and replacement of desktops, printers, \& network devices, such as switches, wiring, \& servers.}
     \resumeItemListEnd     
  	\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\vspace{0.8pt}
\Section{Languages, Certifications, \& Skills}
	\resumeSubHeadingListStart
		\resumeSubItem{Languages}
			{Python, C++, C\#, \LaTeX, Java, Javascript, Haskell, Clingo's ASP, HTML}
\multicomment{\item[]{\textbf{Languages}{: Python, C++, C\#, \LaTeX, Java, Javascript, Haskell, Clingo's ASP, HTML}}}
%		\resumeSubItem{Certifications}
%      		{Dell TechDirect Client}
    	\resumeSubItem{Tools}
      		{Emacs, Vim, Visual Studio, Visual Studio Code, Eclipse, Git, Docker, Adobe Dreamweaver}
      	\resumeSubItem{Frameworks}
      		{.NET Core, Node.js, Electron, Express.js, Windows Presentation Foundation (WPF)}
	\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-6pt}
\Section{Projects}
  \resumeSubHeadingListStart
    
    \resumeSubItem{WebDocker (\href{https://github.com/bremwhit/WebDocker} {github.com/bremwhit/WebDocker})}
    	{An Easy-to-Use, All-Purpose Platform for Running Containers on the Web. The program allows users to create, manage, \& interact with their containers all through a webpage.}
    \begin{itemize}
    	\item[$\circ$] Designed as a full stack web application using Docker, Node.js, Google Firebase, \& NGINX.
    	\item[$\circ$] Created by a 3 person team for a Senior Design Seminar course.
    	\item [$\circ$] $1^{st}$ place at ACM Mid-Southeast Chapter Conference in undergraduate programs.
    \end{itemize}
    
    \resumeSubItem{MESH (\href{https://github.com/Garrett-H/MESH}{https://github.com/Garrett-H/MESH})}
    	{A basic command line Unix shell written to maximize efficiency of memory in the shell. Written to minimize even further the character allocation of Bash. }
    \begin{itemize}
    	\item[$\circ$] Designed as a Terminal default interface application using C, linux standard libraries, \& Makefile.
    	\item[$\circ$] Created by a single person as an attempt to run linux even lighter.
    \end{itemize}
    	
    \resumeSubItem{Leaping Llamas' (\href{https://github.com/Garrett-H/Leapin-Llamas}{github.com/Garrett-H/Leapin-Llamas})}
    	{A side-scrolling game where a player-controlled llama leaps between columns trying not to touch them.}
    \begin{itemize}
    	\item[$\circ$] C\# WPF application using the .NET framework in Visual Studio.
    	\item[$\circ$] Created by a 3 person team for a Senior Software Engineering course.
    \end{itemize}

    \resumeSubItem{THECR (\href{https://github.com/NicholasReid1992/THECR} {github.com/NicholasReid1992/THECR})}
    	{A Simplified Management Solution for assisting UT Martin with the upkeep \& creation of scripts to gather student data for the Tennessee Higher Education Commission (THEC) report.}
    \begin{itemize}
    	\item[$\circ$] C\# console application using the .NET Core framework for an Oracle Database.
    	\item[$\circ$] Developed by a 2 person team for a Senior Design Seminar.
    \end{itemize}
    
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}